
\documentclass[final,1p,times,twocolumn,numbers]{elsarticle}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{float}
\usepackage{nameref}
\usepackage{hyperref, graphicx, wrapfig, booktabs, svg}
\usepackage{bm}
\usepackage{makecell}
\usepackage[dvipsnames]{xcolor}

\usepackage{import}
\usepackage{tikz}
\usepackage{pgfplots}

% \newcommand{\firstround}{\color{blue}}
% \newcommand{\secondround}{\color{Red}}
% \newcommand{\thirdround}{\color{ForestGreen}}

\newcommand{\firstround}{\color{black}}
\newcommand{\secondround}{\color{black}}
\newcommand{\thirdround}{\color{black}}

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}

\journal{NPJ}

\begin{document}

\begin{frontmatter}


\title{Physics Constrained Graph Neural Network for Real Time Prediction of Intracranial Aneurysm Hemodynamics} %% Article title

\author[1]{Vincent Lannelongue} 
\author[1]{Paul Garnier} 
\author[1]{Pablo Jeken-Rico} 
\author[1]{Aurèle Goetz} 
\author[1]{Philippe Meliga} 
\author[2]{Yves Chau} 
\author[1]{Elie Hachem}\corref{{cor1}}
\ead{elie.hachem@minesparis.psl.eu}


\cortext[cor1]{Corresponding author}

%% Author affiliation
\affiliation[1]{organization={Mines Paris - PSL, University Centre for Material Forming (CEMEF) CNRS},
            country={France}}

\affiliation[2]{
    organization={Interventional Neuroradiology Department, Nice University Hospital},
    city={Nice},
    postcode={06100}, 
    state={Alpes-Maritimes},
    country={France}
}


%% Abstract
\begin{abstract}
%% Text of abstract
Intracranial aneurysms (IAs) are life-threatening vascular conditions requiring accurate risk assessment to guide treatment. Hemodynamic biomarkers such as wall shear stress and oscillatory shear index are promising predictors of rupture risk but remain underused clinically due to the high computational cost of traditional CFD methods. We propose a physics-constrained graph neural network (GNN) framework trained on high-fidelity CFD data to predict full 3D, time-resolved hemodynamic fields throughout the cardiac cycle. Our model incorporates enhanced node features and physics-based constraints to capture complex spatio-temporal flow behavior in near real time. It generalizes to varying inflow conditions and unseen patient-specific geometries with no fine-tuning. Additionally, we release a benchmark dataset of 105 patient-derived aneurysm geometries with CFD fields to support the machine learning (ML) community. This is the first GNN model applied to transient 3D aneurysmal flow prediction, paving the way for rapid, AI-driven hemodynamic analysis toward risk stratification and treatment planning.
\end{abstract}


%% Keywords
\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Graph Neural Networks \sep Intracranial Aneurysms 
\sep hemodynamics \sep Computational Fluid Dynamics \sep Machine Learning

\end{keyword}

\end{frontmatter}


\section*{Introduction}
\import{src}{introduction}

\section*{Results}
\import{src}{results}

\section*{Discussion}
\import{src}{discussion}

\section*{Methods} \label{sec:Methods}
\import{src}{methods}

\section*{Data availability} 
The datasets used and analyzed during the current study are available at the following link: \url{https://storage.googleapis.com/large-physics-model/datasets/aneurysm/coarse_03_dataset.zip}
\firstround

\section*{Code availability} 
The underlying code for this study are available from the corresponding author upon reasonable request. \secondround The custom code used for data generation and visualization are relying solely on open-source Python libraries and are available from the corresponding author upon reasonable request as well.
\firstround

\section*{Acknowledgement}
The author(s) declare that financial support was received for the research, authorship, and/or publication of this article. European Union (ERC, CURE, 101045042). The views and opinions expressed are, however, those of the author(s) only and do not necessarily reflect those of the European Union or the European Research Council. Neither the European Union nor the granting authority can be held responsible for them.

\section*{Author contributions}
V. L.: conceptualization, formal analysis, study design, investigation, data curation, software development, methodology, database generation, validation, visualization, writing original draft, review and editing. P.G, P.J.R. and A.G: contributed to software development, database generation, methodology and review. P.M.: contributed to study design, data interpretation, and drafting. Y.C.: provided clinical perspectives to the study, in addition to critically reviewing the manuscript. E.H.: developed the project concept and design, conceptualization, formal analysis, study design, investigation, software development, methodology, validation, visualization, writing original draft, review, editing, secured funding, and revised the manuscript for important intellectual content.

\section*{Competing interests}

The authors declare no competing interests.

\color{black}

 \bibliographystyle{unsrt}
 \bibliography{references}

\end{document}

\endinput
